sentiment-analysis

### 2016-08-02 eda/sentiment-analysis.Rmd
reworked bug

>>>>

Pretty fast. I'll stick to this library and generate five box-plots to see if there's a positive correlation between mean sentiment score and restaurant rating.

```{r, eval = F}
# boxplot for each group
ggplot(reviews_scores) +
  geom_boxplot(aes(stars, sentiment, group = stars)) +
  labs(x = "Business Rating",
       y = "Mean Sentiment Score",
       title = "Mean Sentiment Score vs. Business Rating")

one <- reviews_text %>% 
  filter(stars == 1) %>% 
  group_by(word) %>% 
  count() %>% 
  top_n(200) %>% 
  arrange(n)

wordcloud::wordcloud(one$word, one$n, scale = c(5, 0.5),
                     random.order = F, random.color = F,
                     use.r.layout = T,
                     colors = RColorBrewer::brewer.pal(10, "Reds"))
```
